Analysis of Open Data and Computational Reproducibility in Registered Reports in Psychology

### 2019-09-09 reproducing_registered_reports.Rmd
changes through line 111

To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.

@@

We set out to reproduce the `r length(all_data$doi)` papers that met our inclusion criteria. For each article we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible. These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles. Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which is missing for practically all datasets). We considered data and code to be linked when the manuscript included a unique link to the data and scripts. Ideally, such a link consists of a stable digital object identifier (DOI). A hyperlink to a website that contains the data and script also suffices, although normal hyperlinks are known to break over time [@gertler_reference_2017].

Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code that were part of the article. Linking to data or code does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable. For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data). For three articles the link still worked, but there was no data at the linked destination. For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper. For one paper the data was linked but not available, as the data was embargoed until a future date. Altogether, some data or code was available for `r sum(all_data$availability)` out of `r length(all_data$doi)` papers. For `r sum(all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles the available code contained the statistical analyses, and for `r sum(all_data$data_complete == TRUE, na.rm = TRUE)` all the required data files were available to reproduce the reported results (for `r sum(all_data$data_complete == TRUE & all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles both data and code were available.

>>>>

To find Registered Reports published in psychology, we drew from a database of registered reports maintained by the Center for Open Science.^[https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9] At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports [@hagger_multilab_2016] and Many Labs projects [@klein_investigating_2014; @klein_many_2018]. Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left `r length(all_data$doi)` studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.

@@

We set out to reproduce the findings of `r length(all_data$doi)` papers that met our inclusion criteria. For each article, we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible. These five categories were inspired by FAIR data principles [@wilkinson_fair_2016] that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles. Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which was missing for practically all datasets). We considered data and code to be linked when the manuscript included a unique link to the data and scripts. Ideally, such a link consists of a stable digital object identifier (DOI). A hyperlink to a website that contains the data and script also suffices, although hyperlinks are known to break over time [@gertler_reference_2017]. 
+
Of the `r length(all_data$doi)` papers, `r sum(all_data$linked)` linked to data and/or code that were part of the article. Linking to data or code does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable. For one article the link no longer worked (highlighting the benefit of using a stable DOI for linking to data). For three articles, the link still worked, but there was no data at the linked destination. For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper. For one paper the data was linked but not available, as the data was embargoed until a future date. Altogether, some data or code was available for `r sum(all_data$availability)` of `r length(all_data$doi)` papers. For `r sum(all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles, the available code contained the statistical analyses, and for `r sum(all_data$data_complete == TRUE, na.rm = TRUE)`, all the required data files were available to reproduce the reported results (for `r sum(all_data$data_complete == TRUE & all_data$analysis_script_included == TRUE, na.rm = TRUE)` articles both data and code were available).

### 2019-09-09 reproducing_registered_reports.tex
changes through line 111

To find Registered Reports published in psychology we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018). Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left 62 studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.

@@

We set out to reproduce the 62 papers that met our inclusion criteria. For each article we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible. These five categories were inspired by FAIR data principles (Wilkinson et al., 2016) that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles. Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which is missing for practically all datasets). We considered data and code to be linked when the manuscript included a unique link to the data and scripts. Ideally, such a link consists of a stable digital object identifier (DOI). A hyperlink to a website that contains the data and script also suffices, although normal hyperlinks are known to break over time (Gertler \& Bullock, 2017).

Of the 62 papers, 45 linked to data and/or code that were part of the article. Linking to data or code does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable. For one article the link no longer worked (highlighting the need to use a stable DOI when linking to data). For three articles the link still worked, but there was no data at the linked destination. For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper. For one paper the data was linked but not available, as the data was embargoed until a future date. Altogether, some data or code was available for 43 out of 62 papers. For 37 articles the available code contained the statistical analyses, and for 40 all the required data files were available to reproduce the reported results (for 35 articles both data and code were available.

>>>>

To find Registered Reports published in psychology, we drew from a database of registered reports maintained by the Center for Open Science.\footnote{\url{https://www.zotero.org/groups/479248/osf/items/collectionKey/KEJP68G9}} At the start of this project (06-05-2018) this database consisted of 118 published Registered Reports. Eighty-one articles in this database were published in the psychological literature. We limited our analysis to studies performed by single groups, since such articles are most representative of the researchers currently work, and excluded 7 large scale collaborations where dedicated team members were responsible for making the analysis reproducible, such as Registered Replication Reports (Hagger et al., 2016) and Many Labs projects (Klein et al., 2014, 2018). Upon further inspection of the 72 papers left in the dataset, it turned out that 10 were not formally Registered Reports. This left 62 studies in our sample. When evaluating whether we could reproduce the original results, we limited ourselves to statistical software packages that we had experience with (R, SPSS, Python, MATLAB, and JASP) and excluded studies that required expertise in software packages we are not trained in (e.g., dedicated EEG software), which led to the exclusion of one additional study.

@@

We set out to reproduce the findings of 62 papers that met our inclusion criteria. For each article, we coded whether the data and code were (a) linked, (b) available, (c) not software-specific, (d) understandable, and (e) reproducible. These five categories were inspired by FAIR data principles (Wilkinson et al., 2016) that address the findability, accessibility, interoperability, and reusability of data and code, but we did not explicitly code whether papers adhered to the exact definitions of the four FAIR principles. Our main aim was to examine the reproducibility of results, while adhering to FAIR criteria requires meeting more stringent requirements, for example concerning the presence of metadata (which was missing for practically all datasets). We considered data and code to be linked when the manuscript included a unique link to the data and scripts. Ideally, such a link consists of a stable digital object identifier (DOI). A hyperlink to a website that contains the data and script also suffices, although hyperlinks are known to break over time (Gertler \& Bullock, 2017).
+
Of the 62 papers, 45 linked to data and/or code that were part of the article. Linking to data or code does not mean the data is actually available, and not linking to data in an article does not mean data is unavailable. For one article the link no longer worked (highlighting the benefit of using a stable DOI for linking to data). For three articles, the link still worked, but there was no data at the linked destination. For three articles where there was no link to the data in the article, we were nevertheless able to find data on the Open Science Framework when searching for the title of the paper. For one paper the data was linked but not available, as the data was embargoed until a future date. Altogether, some data or code was available for 43 of 62 papers. For 37 articles, the available code contained the statistical analyses, and for 40, all the required data files were available to reproduce the reported results (for 35 articles both data and code were available).
